Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-11 mtjournal.tex
removed old edpm-paper files, move things to mtjournal name
whoops, correct Spearman's => Pearson's

% [we use weighted correlation to avoid emphasis on short segments
% (which hurts document-level and system-level utility) ]
In figure~\ref{fig:tuneresults}, we plot the Spearman's $r$ (with 95\%
confidence interval) for the results on the two test sets (each
trained on one and tested on the other).
\begin{figure}
  \centerline{{one figure}\qquad{}{two figure}}
  \caption{Figure with two tune-set plots will go here.}
  \label{fig:tuneresults}
\end{figure}

@@

\bibliographystyle{klunamed}
\bibliography{edpm-paper}

>>>>

% [we use weighted correlation to avoid emphasis on short segments
% (which hurts document-level and system-level utility) ]
In figure~\ref{fig:tuneresults}, we plot the Pearson's $r$ (with 95\%
confidence interval) for the results on the two test sets (each
trained on one and tested on the other).
\begin{figure}
  \centerline{{one figure}\qquad{}{two figure}}
  \caption{Figure with two tune-set plots will go here.}
  \label{fig:tuneresults}
\end{figure}

@@

\bibliographystyle{klunamed}
\bibliography{mtjournal}
